\documentclass[/Users/uddhav/Desktop/MA Thesis/Stocks-Responsiveness/LaTex/master_file.tex]{article}
\usepackage[a4paper, margin=0.75in]{geometry}
\usepackage{setspace}    

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}          
\usepackage{mathtools}    
\usepackage{bm}             
\usepackage{dsfont}          
\usepackage{nicefrac}  
\usepackage{hyperref}      

\begin{document}

\begin{itemize}
\item Bennett, B., Stulz, R. M., \& Wang, Z. (2020). \textit{Does joining the S\&P 500 index hurt firms?} (No. w27593). National Bureau of Economic Research.
\item Buss, A., \& Sundaresan, S. (2023). \textit{More risk, more information: How passive ownership can improve informational efficiency.} The Review of Financial Studies, 36(12), 4713-4758.
\item Coles, J. L., Heath, D., \& Ringgenberg, M. C. (2022). \textit{On index investing.} Journal of Financial Economics, 145(3), 665-683.
\item Haddad, V., Huebner, P., \& Loualiche, E. (2021). \textit{How competitive is the stock market? theory, evidence from portfolios, and implications for the rise of passive investing. Theory, Evidence from Portfolios, and Implications for the Rise of Passive Investing.}
\item Investopedia. (2025, October). \textit{The Rise of Exchange-Traded Funds: A Historical Overview}. investopedia.com. \href{https://www.investopedia.com/articles/exchangetradedfunds/12/brief-history-exchange-traded-funds.asp}{https://www.investopedia.com/articles/exchangetradedfunds/12/brief-history-exchange-traded-funds.asp}
\item Kyle, A. S. (1985). \textit{Continuous auctions and insider trading.} Econometrica: Journal of the Econometric Society, 1315-1335.
\item Samson, Marko (2024). \textit{Passive Ownership and Price Informativeness.}
\item von Moltke, F., \& Sløk, T. (2024). \textit{Assessing the Impact of Passive Investing over Time: Higher Volatility, Reduced Liquidity, and Increased Concentration.}
\item Weller, B. M. (2018). \textit{Does algorithmic trading reduce information acquisition?}. The Review of Financial Studies, 31(6), 2184-2226.
\item William F. Sharpe (1991) \textit{The Arithmetic of Active Management}, Financial Analysts Journal, 47:1, 7-9, DOI: 10.2469/faj.v47.n1.7
\end{itemize}

\end{document}